Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-12 lab/report/include/lab1.tex
written some text

\subsubsection*{Benchmark 2 - No sharing}
This benchmark have no sharing of the counter array. The counter array is divided up equally among the threads and a thread only increments the values in it's assigned array elements. A barrier is placed before a new incrementation lap of the assigned array elements begins.

\subsubsection*{Benchmark 3 - All shared}
In this benchmark, the counter array is shared among all threads. Each thread increments every element in the counter array while in mutual exclusion. A lock is used to provide mutual exclusion and a barrier is placed after all threads have incremented.

@@

In the producer consumer benchmark, the reading threads transition the data element to the E state when accessing the array for the first time if the writing thread have not accessed it already. However, the whole counter array is shared and thus will not the E state be of any gain. Therefore, MSI and MESI performs equally regardless of working set size, which is shown in \reffig{fig:resultslab1}.

\begin{figure}[t]
	\center
	\includegraphics[width=0.7\textwidth]{bars}
	\caption{Simulation results using various cache coherent protocols combined with different working sets and benchmarks.}
	\label{fig:resultslab1}
\end{figure}

>>>>

\subsubsection*{Benchmark 2 - No sharing}
This benchmark have no sharing of the counter array. The counter array is divided up equally among the threads, giving each thread access to every nth counter element, where n is the number of threads. Each thread then increments it's assigned counters sequentially. A barrier is placed before a new incrementation lap of the assigned array elements begins.

\subsubsection*{Benchmark 3 - All shared}
In this benchmark, the counter array is shared among all threads. Each thread increments every element in the counter array sequentially while in mutual exclusion. A lock is used to provide mutual exclusion and a barrier is placed after all threads have incremented.

@@

In the producer consumer benchmark, the reading threads transition the data element to the E state when accessing the array for the first time if the writing thread have not accessed it already. However, the whole counter array is shared and thus will not state E be of any gain. Therefore, MSI and MESI performs equally regardless of working set size, which is shown in \reffig{fig:resultslab1}.

In the no sharing benchmark the first read access to every element end in state S for MSI and state E for MESI, respectively. The following write transitions the element to state M for both the CCPs, but MSI have to issue a BusUpdate whereas MESI's transition is costless. The BusUpdate broadcasts an invalidate signal which gives MSI a slight reduction in performance compared to MESI. In the small working set the elements will stay in state M to the end of execution, but in the larger working sets the element is fetched from LLC upon each read access due to cache trashing. This makes MSI issue an invalidate broadcast for each incrementation and the accumulated overhead is easily spotted in \reffig{fig:resultslab1}, it is also seen that the overhead become linearly to the size of the working set.

\begin{figure}[t]
	\center
	\includegraphics[width=0.7\textwidth]{bars}
	\caption{Simulation results using various cache coherence protocols combined with different working sets and benchmarks.}
	\label{fig:resultslab1}
\end{figure}
